\documentclass[../main.tex]{subfiles}

\begin{document}
Our design does not provide protection against Denial of Service attacks and
we consider this attack vector as being out of scope. We were initially
concerned that our use of blocking I/O operations on the named pipe interface
exposes a DoS vulnerability. In case the non-enclave process gets owned, an
adversary can launch a DoS attack by writing arbitrary bytes in the named
pipe used for interprocess communication. This would cause the enclave or
non-enclave process to either block on read(), if less than the expected bytes
exist in the pipe, or exit due to a logical error introduced by the arbitrary
bytes read. A more sophisticated implementation of the named pipe interface
would be to use asynchronous I/O operations with timeouts as signals to proceed
with serving the next request. This would only make our design a bit more
resilient to such attacks, though still not invulnerable. The threat model we
are considering implies that everything running outside the enclave can be
potentially owned. Thus, an adversary that takes control of the hypervisor or
the host OS, has way more trivial choices on how to launch a DoS attack such
as blocking the NIC from incoming packets or even shutting down the machine
itself, than writing an exploit destined for our named pipe interface. It is
clear, our compartmentalization of the openssl library does not provide any
additional conveniences for the attacker to launch a DoS attack. Also,
a DoS attack only constitutes a liveness threat, rather a privacy threat, which
fully complies with SGX's native goal of providing confidentiality and
integrity guarantees.
\end{document}
