\documentclass[../main.tex]{subfiles}
 
\begin{document}

\textit{Project Management. Outline of how the work was split up. How
collaborative work was planned. Who did what. How agreement was reached. How
essential project information was managed and communicated. How integration
and testing was organised.}\\

\noindent
At the begining of the project we have spent about 2 weeks making sure we
understand the problem and our approach to the solution. We researched
software possibilities, available documentation, related work until we
identified three main parts of the project:

\begin{itemize}
	\item Secret provinsioning to the enclave through reomte attestation
	\item Libressl and nginx instrumentation
	\item Performance evaluation
\end{itemize}

% add something on milestones, risks, main goals, seocndary goals (gant chart)
\noindent
Therefore, we divided our group into three subgroups:
\begin{itemize}
	\item Ahmed and John working on the SGX part
	\item Betran and Wiktor working on Libressl and nginx
	\item Chiraphat working on the test setup and performance evaluation
\end{itemize}

\noindent
We have chosen messaging app Slack as our daily communication channel since we
already used it during the course duration. We setup github repositories to
collaborate on the code. We also decided to use LaTex for documentation of our
work and writeup of group report to follow research best practices.\\

\noindent
Every week we met with Brad, our supeervisor, to report on our progress, make
sure we are on track with our schedule and discuss any issues and tasks to be
carried in the following week. Additionally, we held our own meeting to
internally share what we have learned and (re)distribute further work.\\

\noindent
We also assessed whether some tasks need more man power, which for most of the
time was not necessary, until towards the end of the project when we stumbled
upon more challenging implementation issues or needed to integrate parts of
the project to be ready for final preformance evaluation. During that time we
held more in person meetings and held pair debugging sessions. These turned
out to be very useful and we managed to solve the issues on time.

\end{document}